Paper # 1 - Figures

### 2020-03-16 papers/paper-1/paper_1_figures.Rmd
v1 of the paper done

plot_theme <- theme_bw()

@@

# EU countries
eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]

# EU overseas territories
eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]

# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
```

@@

```{r}
effort_binned <- effort_binned_good_fishing_vessels_2018 %>%
  mutate(is_eu = case_when(flag %in% c(eu_countries, eu_territories) ~ TRUE,
                           TRUE ~ FALSE),
         is_usa = case_when(flag %in% c(us_territories, "USA") ~ TRUE,
                            TRUE ~ FALSE),
         new_flag = case_when(is_eu ~ "EU", 
                              is_usa ~ "USA", 
                              TRUE ~ flag))

@@

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category) %>%
  summarize(subs = sum(value, na.rm = T)) %>%
  spread(category, subs) %>%
  rename(A_subs = A,
         B_subs = B,
         C_subs = C)
```

```{r}
# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
         tot_subs_KWh = (A_subs+B_subs+C_subs)/fishing_KWh_lat_lon) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

# Apply subsidy rates to binned effort
effort_binned_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag")
```

@@

```{r}
median_breaks <- seq(0,6, by = 1)
median_limits <- c(0,6)
median_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

median_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = median_limits, 
                       breaks = median_breaks,
                       labels = median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

@@

median_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = med_B_subs_KWh), color = "#000000") +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_median_limits, 
                       breaks = region_median_breaks,
                       labels = region_median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

@@

```{r}
mean_breaks <- seq(0,6, by = 1)
mean_limits <- c(0,6)
mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                     na.value = "#000000", 
                     limits = mean_limits, 
                     breaks = mean_breaks,
                     labels = mean_labels,
                     oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
```

```{r}
mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity ($/KWh)", 
                       na.value = "#000000", 
                       limits = mean_limits, 
                       breaks = mean_breaks,
                       labels = mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
```

@@

weighted_mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = weighted_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = weighted_mean_limits, 
                       breaks = weighted_mean_breaks,
                       labels = weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

weighted_mean_subsidy_intensity_B_grid_map

ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
```

@@

weighted_mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = weighted_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_weighted_mean_limits, 
                       breaks = region_weighted_mean_breaks,
                       labels = region_weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

weighted_mean_subsidy_intensity_B_region_map

ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
```

### Stock status

>>>>

plot_theme <- theme_bw()+
  theme(legend.text = element_text(color = "black", size = 16),
        legend.title = element_text(color = "black", size = 16),
        legend.title.align = 1,
        legend.direction = "horizontal",
        legend.position = "bottom",
        legend.justification = "center",
        axis.text = element_text(color = "black", size = rel(1)))

@@

# Netherlands overseas territories
nld_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NLD"]

# France overseas territories
fra_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "FRA"]

# Denmark overseas territories
dnk_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "DNK"]

# British overseas territories
gbr_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "GBR"]

# Norway overseas territories
nor_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]

# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
usa_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]

# Australian overseas territories: Christmas Island
aus_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "AUS"]
```

@@

```{r}
effort_binned <- effort_binned_good_fishing_vessels_2018 %>%
  mutate(new_flag = case_when(flag %in% nld_territories ~ "NLD",
                              flag %in% fra_territories ~ "FRA",
                              flag %in% dnk_territories ~ "DNK",
                              flag %in% gbr_territories ~ "GBR",
                              flag %in% nor_territories ~ "NOR",
                              flag %in% usa_territories ~ "USA",
                              flag %in% aus_territories ~ "AUS",
                              flag == "COK" ~ "NZL", # for now assign cook islands to new zealand
                              TRUE ~ flag))

@@

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category) %>%
  summarize(subs = sum(value, na.rm = T)) %>%
  spread(category, subs) %>%
  rename(A_subs = A,
         B_subs = B,
         C_subs = C) %>%
  mutate(BC_subs = B_subs + C_subs,
         tot_subs = A_subs + B_subs + C_subs)
```

```{r}
# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
         BC_subs_KWh = BC_subs/fishing_KWh_lat_lon,
         tot_subs_KWh = tot_subs/fishing_KWh_lat_lon) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

# Apply subsidy rates to binned effort
effort_binned_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag")

# Summarize by lat/lon
subsidy_intensity_binned <- effort_binned_sub_intensity %>%
  group_by(lat_bin_center, lon_bin_center) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))

# Summarize by fao region
subsidy_intensity_region <- effort_binned_sub_intensity %>%
  group_by(fao_region) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
```

@@

```{r}
median_breaks <- seq(0,8, by = 2)
median_limits <- c(0,8)
median_labels <- c("0", "2", "4", "6", paste0("\u2265","8"))

# Total subsidies
median_subsidy_intensity_tot_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_tot_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = median_limits, 
                       breaks = median_breaks,
                       labels = median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_tot_grid_map

ggsave(paste0(results_dir, "median_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Bad subsidies only
median_subsidy_intensity_B_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = median_limits, 
                       breaks = median_breaks,
                       labels = median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

# Bad and ambiguous subsidies
median_subsidy_intensity_BC_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_BC_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = median_limits, 
                       breaks = median_breaks,
                       labels = median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_BC_grid_map

ggsave(paste0(results_dir, "median_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)

@@

# Total subsidies
median_subsidy_intensity_tot_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = med_tot_subs_KWh), color = "#000000") +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_median_limits, 
                       breaks = region_median_breaks,
                       labels = region_median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_tot_region_map

ggsave(paste0(results_dir, "median_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Bad subsidies
median_subsidy_intensity_B_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = med_B_subs_KWh), color = "#000000") +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_median_limits, 
                       breaks = region_median_breaks,
                       labels = region_median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

# Ambiguous and Bad subsidies
median_subsidy_intensity_BC_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = med_BC_subs_KWh), color = "#000000") +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_median_limits, 
                       breaks = region_median_breaks,
                       labels = region_median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_BC_region_map

ggsave(paste0(results_dir, "median_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)

@@

```{r}
mean_breaks <- seq(0,8, by = 2)
mean_limits <- c(0,8)
mean_labels <- c("0", "2", "4", "6", paste0("\u2265","8"))

# Total subsidies 
mean_subsidy_intensity_tot_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_tot_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                     na.value = "#000000", 
                     limits = mean_limits, 
                     breaks = mean_breaks,
                     labels = mean_labels,
                     oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_tot_grid_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Bad subsidies 
mean_subsidy_intensity_B_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                     na.value = "#000000", 
                     limits = mean_limits, 
                     breaks = mean_breaks,
                     labels = mean_labels,
                     oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

# Bad and ambiguous subsidies 
mean_subsidy_intensity_BC_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_BC_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                     na.value = "#000000", 
                     limits = mean_limits, 
                     breaks = mean_breaks,
                     labels = mean_labels,
                     oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_BC_grid_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
```

```{r}
# Tot subs
mean_subsidy_intensity_tot_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = mean_tot_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = mean_limits, 
                       breaks = mean_breaks,
                       labels = mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_tot_region_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Bad subs
mean_subsidy_intensity_B_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = mean_limits, 
                       breaks = mean_breaks,
                       labels = mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

@@

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)

# Bad and ambiguous subs
mean_subsidy_intensity_BC_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = mean_BC_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = mean_limits, 
                       breaks = mean_breaks,
                       labels = mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_BC_region_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
```

@@

# Tot subs
w_mean_subsidy_intensity_tot_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = w_mean_tot_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = weighted_mean_limits, 
                       breaks = weighted_mean_breaks,
                       labels = weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

w_mean_subsidy_intensity_tot_grid_map

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Bad subs
w_mean_subsidy_intensity_B_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = w_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = weighted_mean_limits, 
                       breaks = weighted_mean_breaks,
                       labels = weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

w_mean_subsidy_intensity_B_grid_map

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

# Bad and ambiguous subs
w_mean_subsidy_intensity_BC_grid_map <- subsidy_intensity_binned %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = w_mean_BC_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = weighted_mean_limits, 
                       breaks = weighted_mean_breaks,
                       labels = weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

w_mean_subsidy_intensity_BC_grid_map

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
```

@@

# Tot subs
w_mean_subsidy_intensity_tot_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = w_mean_tot_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_weighted_mean_limits, 
                       breaks = region_weighted_mean_breaks,
                       labels = region_weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

w_mean_subsidy_intensity_tot_region_map

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Bad subs
w_mean_subsidy_intensity_B_region_map <- subsidy_intensity_region %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = w_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_weighted_mean_limits, 
                       breaks = region_weighted_mean_breaks,
                       labels = region_weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

w_mean_subsidy_intensity_B_region_map

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
